Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd
added national poll in data

>>>>

National polls is another newly created variable in our dataset, represented by a binary
indicator (1 for national polls, 0 otherwise). This distinction is important because
not all polls are conducted nationally; some are state-specific and may reflect the
region's preference for a particular presidential candidate. Ignoring this distinction
may introduce significant bias into our model. By labeling each poll as national or
non-national, we can give higher weight to national polls, which are more representative
of overall public opinion, and thus improve the accuracy of our predictive model.
